---
title: "portfolio-7"
author: "Elayna Seago"
date: "4/19/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

My goal in this lab is to use to make a map graph. I made one with the USArrests map that were given as part of an example on making map graphs and then I did it with Tidy Tuesday bee data (which I also used before)

```{r read-bee-data}
colony <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-01-11/colony.csv')
stressor <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-01-11/stressor.csv')
```


```{r}
library(tidyverse) 
```



```{r filter}
colony_2015 <- colony %>%              
  filter(
    year == "2015" ,
    months == "January-March" ,
    state != "Other States" ,
    state != "United States"
  )

colony_2015
```

Using example code and example dataset
```{r murders-map}
data <- data.frame(murder = USArrests$Murder,
m_state = tolower(rownames(USArrests)))
m_map <- map_data("state")
k <- ggplot(data, aes(fill = murder))

k+geom_map(aes(map_id = m_state), map = m_map)+
  expand_limits(x = m_map$long, y = m_map$lat)
```

using bee data and tweaking code
```{r bee-map-1}
bee_data <- data.frame(pct_loss = colony_2015$colony_lost_pct,
bee_state = tolower(colony_2015$state))
bee_map <- map_data("state")
b <- ggplot(bee_data, aes(fill = pct_loss))

b+geom_map(aes(map_id = bee_state), map = bee_map)+
  expand_limits(x = bee_map$long, y = bee_map$lat)

```


making more changes- seems like making na gray didn't work?
```{r bee-map-2}
bee_data <- data.frame(pct_loss = colony_2015$colony_lost_pct,
bee_state = tolower(colony_2015$state))
bee_map <- map_data("state")
b <- ggplot(bee_data, aes(fill = pct_loss))

b+geom_map(aes(map_id = bee_state), map = bee_map)+
  expand_limits(x = bee_map$long, y = bee_map$lat)+
  scale_fill_continuous(name="Percent Loss", 
            low = "lightgreen", high = "darkgreen",limits = c(0,40), 
            breaks=c(5,10,15,20,25,30,35), na.value = "grey50")
```

Alternate maps! 

```{r}
library(maps)
```

```{r}
MainStates <- map_data("state")
```


```{r counties}
AllCounty <- map_data("county")
ggplot() + geom_polygon( data=AllCounty, aes(x=long, y=lat, group=group),
                color="darkblue", fill="lightblue", size = .1 ) +
  
          geom_polygon( data=MainStates, aes(x=long, y=lat, group=group),
                color="black", fill="lightblue",  size = 1, alpha = .3)
```

"Blevins, Cameron; Helbock, Richard W., 2021, "US Post Offices", https://doi.org/10.7910/DVN/NUKCNA, Harvard Dataverse, V1, UNF:6:8ROmiI5/4qA8jHrt62PpyA== [fileUNF]"


```{r}
post_offices <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-04-13/post_offices.csv')

```

```{r}
post_offices
```

```{r filter-post-office}
graph_post_offices <- post_offices %>%              
  filter(
    coordinates == "TRUE" ,
    duration > 150
  )

graph_post_offices
```


I layered the location of very old post offices on this map. Also it seems like latitude and longitude are reversed but the other way looks incorrect
```{r post-office-map}
AllCounty <- map_data("county")
ggplot() + geom_polygon( data=AllCounty, aes(x=long, y=lat, group=group),
                color="darkblue", fill="lightblue", size = .1 ) +
  
          geom_polygon( data=MainStates, aes(x=long, y=lat, group=group),
                color="black", fill="lightblue",  size = 1, alpha = .3)+
           
          geom_point(data = graph_post_offices, aes(x = longitude , y = latitude))
```




